PANCHANGE_data_preprocessing

### 2020-08-31 PANCHANGE_data_preprocessing2020-07-15.Rmd
investigating none of the above

```{r}
mhd.raw.id %>%
  select(
    control,
    mhd.none_of_the_above,
    mhd.none_of_the_above.1
  )

mhd.raw.id %>%
  group_by(mhd.none_of_the_above.1) %>%
  count(
    control,
    mhd.none_of_the_above
  )

mhd.raw.id %>%
  count(
    control,
    age_
  )
```

>>>>

```{r}
if(RAMP == TRUE) {
mhd.raw.id %>%
  select(
    control,
    mhd.none_of_the_above,
    mhd.none_of_the_above.1
  )

mhd.raw.id %>%
  group_by(control) %>%
  count(
    mhd.none_of_the_above.1,
    mhd.none_of_the_above
  )

mhd.raw.id %>%
  count(
    control,
    age_
  )
}
```

Inspect the participants that do not qualify as double "None of these"
```{r}
if(RAMP == TRUE) {
mhd.raw.id %>%
  filter(
    (mhd.none_of_the_above.1 == "Not None of these" |
    mhd.none_of_the_above == "Not None of these") &
      control == "Control"
  )
}
```
